Relationships in the extremes and their influence on competition and coexistence

### 2021-09-07 paper/Paper.Rnw
intro editing

To demonstrate plausibility of ATA altering coexistence between species, we carried out long time scale simulations using a simple two-species lottery model. Environmental variability has been classically shown to promote coexistence via storage mechanisms in a temporal lottery model of competition \citep{Chesson_1981, Warner_1985}, hence we continue/move forward with this simple model to examine the effect of extreme relationships between environmental responses on the contribution of storage effects to coexistence. We simulated two different communites up to \Sexpr{M} time steps to hopefully make it clear to the reader than ATA makes a difference (see figure \ref{fig:pedagog}). The only distinction between the two simulations is that one depends on asymmterically tail associated temporal dynamics and one does not. Markedly, the simulation with ATA has longer periods of one-species dominance than the simulation without, almost X times as much....

>>>>

To demonstrate plausibility of ATA altering coexistence between species, we carried out long time scale simulations using a simple two-species lottery model. Environmental variability has been classically shown to promote coexistence via storage mechanisms in a temporal lottery model of competition \citep{Chesson_1981, Warner_1985}, hence we move forward with this simple model to examine the effect of extreme relationships between environmental responses on the contribution of storage effects to coexistence. We simulated two different communites up to \Sexpr{M} time steps to hopefully make it clear to the reader that ATA makes a difference for competition and coexistence between species (see figure \ref{fig:pedagog}). The only distinction between the two simulations is that one depends on asymmterically tail associated temporal dynamics and one does not. Markedly, the simulation with ATA has longer periods of one-species dominance than the simulation without, implying less recoverablility when rare and thus less coexistence \citep{Chesson_2000} when environmentally dependent variables are asymmetrically tail associated.
